---
output: pdf_document
---
---
title: "DATA 607 Assignment 3"
author: "Md Jalal Uddin"
date: "September 18, 2016"
--------------------------

Problem 3. 
Copy the introductory example. The vector name stores the extracted names.

```{r}
library(stringr)
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555
-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}")) #Source:Automated Data Collecton wit R, section 8.1.1, page 198
name

```

(a) Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.
```{r}
name1 <- sub(" [A-z]{1}\\. "," ",name)  # remove initials
name1 
# Source:http://stackoverflow.com/questions/33826650/last-name-first-name-to-first-name-last-name
name2 <- sub("(\\w+),\\s(\\w+)","\\2 \\1", name1) # switch last,first to first last

name2

name3 <- sub("[A-z]{2,3}\\. ","",name2)  
#remove titles
name3
```

(b) Construct a logical vector indicating whether a character has a title.

```{r}

Show_title<-str_detect(name,"[[:alpha:]]{2,}\\.") #Source:Automated Data Collecton wit R, section 8.1.2, page 205
title <- data.frame(name,Show_title)
title

```
c. Construct a logical vector indicating whether a character has a second name

```{r}
Second_name <- str_detect(name," [A-z]\\.{1}")
Second <- data.frame(name,Second_name)
Second
#Source:Automated Data Collecton wit R, section 8.2.1, page 209

```

Problem 4:Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.
(a) [0-9]+\\$
(b) \\b[a-z]{1,4}\\b
(c) .*?\\.txt$
(d) \\d{2}/\\d{2}/\\d{4}
(e) <(.+?)>.+?</\\1>


(a) [0-9]+\\$

```{r}
raw<- "I love new york.56967$ NY- 11/34/7453, 587932$, 30032$"
str_extract(raw, "[0-9]+\\$")
str_extract_all(raw, "[0-9]+\\$")

```
Description: take any digit from zero to nine and any number of digit with dollar sign. the example is given above. 

(b) \\b[a-z]{1,4}\\b
```{r}
raw<- "Ryan love New Youk. I love New york.56967$ NY-567456, born- 11/34/7453, 587932$, bercelona4b"

str_extract(raw, "\\b[a-z]{1,4}\\b")
str_extract_all(raw, "\\b[a-z]{1,4}\\b")

```
Description: It will give us any letter with at least 1 but not more than 4 letter word with all small letter.  

(c) .*?\\.txt$
```{r}
raw<- " Ryan love New Youk. I love New york.56967$ NY-567456,  lock_dplyr_fake.rmt.txt"

str_extract(raw, ".*?\\.txt$")
str_extract_all(raw, "\\.txt$")


```



(d) \\d{2}/\\d{2}/\\d{4}

```{r}
raw<- "I love new york.56967$ NY-11-32-4567, born- 11/08/1993, 587932$, 30032$"
str_extract(raw, "\\d{2}/\\d{2}/\\d{4}")
str_extract_all(raw, "\\d{2}/\\d{2}/\\d{4}")

```
Description: the above expression give the date with the following format 11/11/1111


(e) <(.+?)>.+?</\\1>

```{r}
raw<- " Ryan love a. I love New york.56967$ NY-567456, born- 11/34/7453, 5.6/9 587932$, 0.123$  abc201 $101 1/1 "

str_extract(raw, "<(.+?)>.+?</\\1>")


```



(9) The following code hides a secret message. Crack it with R and regular expressions.

clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5 Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgn b.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

```{r}
secret <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdijLj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

```

Solution:

```{r}
#Seperating all the capital letter.
Pattern <- unlist(str_extract_all(secret, "[[:upper:].]")) #Source:Automated Data Collecton wit R, Table 8.4, page 208
Pattern 

Pattern <- paste(Pattern, sep=" ", collapse="")
# remove all the "" 
Pattern

```




